A SIMPLE MODEL FOR LITERARY ANALYSIS BY TEXT ANALYTICS: COMPARATIVE APPROACH AND EXAMPLE ON JAMES JOYCE AGAINST SHAKESPEARE AND THE BIBLE

### 2017-08-18 latex/article.tex
finished final touches before sending it to peers

Figures~\ref{fig:pca1},~\ref{fig:pca2} and~\ref{fig:pca3} exposes the works of Joyce and
Shakespeare and the Bible books within the principal components.
As the second and third component held very near spreads (absolute values of the corresponding eigenvalues),
and the first two components summed only $\approx 50\%$ of all dispersion,
we chose to use the first three components (in contrast to using only the first two components as is usual for PCA).
As can be noticed, Joyce's works are very distinct from Shakespeare,
and some of them are also very distinct from Bible books.
Nevertheless, some of them fall near Bible books.

>>>>

Figures~\ref{fig:pca1},~\ref{fig:pca2} and~\ref{fig:pca3} exposes the works of Joyce and
Shakespeare and the Bible books within the principal components.
As the second and third component held near spreads\footnote{The
amount of dispersion in each component is:
$\approx 40.25,\; 14.32,\; 11.91\%$ and then values bellow $9\%$.} (absolute values of the corresponding eigenvalues),
and the first two components summed only $\approx 50\%$ of all dispersion,
we chose to use the first three components (in contrast to using only the first two components as is usual for PCA).
As can be noticed, Joyce's works are very distinct from Shakespeare,
and some of them are also very distinct from Bible books.
Nevertheless, some of them fall near Bible books.
